\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{latexsym}
\usepackage{verbatim}
\usepackage{array}
\usepackage{enumitem}
\usepackage{academicons}

\setlength{\multicolsep}{-3pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0in}

\input{glyphtounicode}

\definecolor{GlacierBlue}{RGB}{70,150,180}
% \definecolor{SpringWater}{RGB}{93,190,138}
% \definecolor{StarNight}{RGB}{82,82,136}

% Page style
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

% URL style
\urlstyle{same}

% Paragraph and alignment settings
\raggedbottom
\raggedright

% Section formatting
\titleformat{\section}{
    \vspace{-5pt}\color{GlacierBlue}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{GlacierBlue}\titlerule\vspace{-5pt}]

% PDF accessibility
\pdfgentounicode=1

\setlist[enumerate,1]{%
    label=\color{Gray}[ \arabic* ],  % Gray brackets and number
    labelwidth=3em,   % Wide enough for [ 100 ]
    labelsep=1em,     % Space between label and text
    labelindent=0pt,  % Align label to margin
    leftmargin=4em,   % labelwidth + labelsep
    align=left,
    itemsep=0pt
}

% Custom commands
%------------------------- Heading / Section Macros -------------------------
\newcommand{\resumeSubSection}[1]{%
  {\noindent\color{GlacierBlue}\scshape\large #1 \dotfill} \vspace{-6pt}
}

%------------------------- Item List Macros -------------------------
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{%
    \begin{itemize}[leftmargin=12pt, label={\color{GlacierBlue}$\circ$}, itemsep=1pt, topsep=1pt]
}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeItem}[1]{%
    \item \footnotesize{#1\vspace{0pt}}
}
\newcommand{\resumeSubItem}[1]{%
    \resumeItem{#1}\vspace{-4pt}
}

%------------------------- Education, Work, Teaching Subheadings -------------------------
\newcommand{\resumeEduSubheading}[3]{%
    \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textbf{\small #2 {\color{GlacierBlue} \textbullet} #3} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeWorkSubheading}[4]{%
    \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}, #2 & \textbf{\small #3 {\color{GlacierBlue} \textbullet} #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeTeachSubheading}[4]{%
    \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}, #2 & \textbf{\small #3 {\color{GlacierBlue} \textbullet} #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeResearchAdvisorSubheading}[2]{%
    \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}, #2 \\
    \end{tabular*}\vspace{-4pt}
}

%------------------------- Mentorship List Macros -------------------------
\newcommand{\resumeMenteeItemListStart}{%
    \begin{itemize}[leftmargin=0pt, label={}]
    \vspace{-5pt}
}
\newcommand{\resumeMenteeItemListEnd}{%
    \end{itemize}\vspace{-5pt}
}

\newcommand{\resumeMenteeItem}[3]{%
    \item
	\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        {{\color{GlacierBlue}\faPortrait} #1} & \textbf{\small #2 {\color{GlacierBlue} \textbullet} #3} \\
    \end{tabular*}\vspace{2pt}
}

\newcommand{\resumeMenteeProject}[1]{%
    { \textit{#1} \par}\vspace{-2pt}
}

\newcommand{\resumeMenteeDescription}[1]{%
    { {#1} \par}\vspace{-2pt}
}

%------------------------- Publications -------------------------
\newcommand{\resumePubListStart}{%
    \begin{enumerate}
}
\newcommand{\resumePubListEnd}{%
    \end{enumerate}
}

\newcommand{\resumePubItem}[2]{%
    \item {#1 {\color{GlacierBlue}#2}}
}

%------------------------- Engagement -------------------------
\newcommand{\resumeEngagementItemListStart}{%
    \begin{itemize}[leftmargin=0pt, label={}]\vspace{0pt}
}
\newcommand{\resumeEngagementItemListEnd}{%
    \end{itemize}\vspace{6pt}
}

\newcommand{\resumeEngagementItem}[3]{%
    \item
    {\color{GlacierBlue}$\circ$} 
    \begin{tabular*}{\dimexpr\linewidth-9pt\relax}[t]{@{\extracolsep{\fill}}l r}
        #1 & {\small #2} \\
        \multicolumn{2}{@{}l}{at \textit{#3}}
    \end{tabular*}\vspace{-8pt}
}

%------------------------- Awards -------------------------
\newcommand{\resumeAwardItemListStart}{%
    \begin{itemize}[leftmargin=0pt, label={}]\vspace{0pt}
}
\newcommand{\resumeAwardItemListEnd}{%
    \end{itemize}\vspace{6pt}
}

\newcommand{\resumeAwardItem}[3]{%
    \item
    {\color{GlacierBlue}$\circ$} 
    \begin{tabular*}{\dimexpr\linewidth-9pt\relax}[t]{@{\extracolsep{\fill}}l r}
       { {#1} {\small\color{GlacierBlue} \textit{by} }{\small \textit{#2}}} & {\small#3}
    \end{tabular*}\vspace{-8pt}
}


%---------- Document Starts ----------
\begin{document}

% Heading
\begin{center}
    {\Huge \scshape \color{GlacierBlue} Ronghao Zhang} \\
    \vspace{5pt}
    {\color{gray} Whitehead Biomedical Research Building, 615 Micheal Street, Atlanta, GA 30332} \\
    \vspace{0pt}
    \small
    \href{mailto:ronghao.zhang.academic@gmail.com}{{\color{gray}\faPaperPlane} \color{GlacierBlue} ronghao.zhang.academic@gmail.com} ~
    \href{https://linkedin.com/in/ronghao-zhang-a81b05234}{{\color{gray}\faLinkedin} \color{GlacierBlue} ronghao-zhang-a81b05234} ~
    \href{https://ronghao-zhang.github.io/}{{\color{gray}\faGithub} \color{GlacierBlue} ronghao-zhang.github.io} ~
	\href{https://orcid.org/0000-0001-6418-090X}{{\color{gray}\faOrcid} \color{GlacierBlue} 0000-0001-6418-090X}
    \vspace{1pt}
\end{center}

% Education
\section{EDUCATION}
	\resumeSubHeadingListStart
		\resumeEduSubheading
			{Georgia Institute of Technology \& Emory University}{Atlanta, GA}{2023 -- 2028 (Expected)}
			\resumeItemListStart
				\resumeItem{Ph.D. student in Biomedical Engineering, Wallace H. Coulter Department of Biomedical Engineering}
				\resumeItem{\textit{(Tentitive) Research Focus:} Cortical processing of touch signals and contribution to tactile behavior in health and disease}
				\resumeItem{\textit{Adviser:} Dr. Alan Emanuel, Department of Cell Biology, Emory University School of Medicine}
			\resumeItemListEnd

		\resumeEduSubheading
			{Case Western Reserve University}{Cleveland, OH}{2019 -- 2023}
			\resumeItemListStart
				\resumeItem{Bachelor of Science in Systems Biology, Bachelor of Arts in Computer Science, \textit{Summa Cum Laude}}
			\resumeItemListEnd
	\resumeSubHeadingListEnd

% WORK EXPERIENCE
\section{WORK EXPERIENCE}
	\resumeSubHeadingListStart
		\resumeWorkSubheading
			{Emory University School of Medicine}{Research Assistant}{Atlanta, GA}{2023 -- Present}
			\resumeItemListStart
				\resumeItem{\textit{Adviser}: Dr. Alan Emanuel, Department of Cell Biology}
			\resumeItemListEnd

		\resumeWorkSubheading
			{University of Chicago}{Research Assistant}{Chicage, IL}{Summer, 2022}
			\resumeItemListStart
				\resumeItem{\textit{Adviser}: Dr. Sliman Bensmaia, Department of Organismal Biology and Anatomy}
			\resumeItemListEnd

		\resumeWorkSubheading
			{Case Western Reserve University School of Medicine}{Research Assistant}{Cleveland, OH}{2019 -- 2023}
			\resumeItemListStart
				\resumeItem{\textit{Adviser}: Drs. Jeffrey Garvin \& Agustin Gonzalez-Vincente, Department of Physiology and Biophysics}
			\resumeItemListEnd
	\resumeSubHeadingListEnd

% TEACHING & ADVISING EXPERIENCE
\section{TEACHING \& ADVISING EXPERIENCE}
	\resumeSubSection{Research Advising and Mentoring}
		\resumeSubHeadingListStart
			\resumeResearchAdvisorSubheading
				{Undergraduate Research Projects}{Research Mentor}
				\vspace{-12pt}
				\resumeMenteeItemListStart
					\resumeMenteeItem
						{Ruorong Qi}{Emory University}{2024 -- Present}
						\resumeMenteeProject{Progression of abnormal signaling in primary somatosensory cortex of MitoPark mice.}
						\resumeMenteeDescription{Ruorong was selected as a Petit Lanier scholar in 2024 for this work and was funded by the Sartain Lanier Foundation in 2025 to continue this research.}
				\resumeMenteeItemListEnd
		\resumeSubHeadingListEnd

	\resumeSubSection{Teaching}
		\resumeSubHeadingListStart
			\resumeTeachSubheading
				{Biomed. Data Visual. (BMED8813)}{Teaching Assistant}{Georgia Institute of Technology}{Spring, 2025}
				\vspace{-12pt}
			\resumeTeachSubheading
				{Optical Microscopy (BMED6785)}{Teaching Assistant}{Georgia Institute of Technology}{Fall, 2024}
				\vspace{-12pt}
			\resumeTeachSubheading
				{Intro. to Neurobiology (BIOL373)}{Teaching Assistant}{Case Western Reserve University}{Fall, 2022}
				\vspace{-12pt}
			\resumeTeachSubheading
				{Dynamics of Bio. Systems (BIOL300)}{Teaching Assistant}{Case Western Reserve University}{Spring, 2022}
				\vspace{-12pt}
			\resumeTeachSubheading
				{Elementary Programming (ENGR131)}{Teaching Assistant}{Case Western Reserve University}{Fall, 2021}
				\vspace{-12pt}
			\resumeTeachSubheading
				{Genes, Evolution \& Ecology (BIOL214)}{Teaching Assistant}{Case Western Reserve University}{Fall, 2021}
				\vspace{-12pt}
		\resumeSubHeadingListEnd

% PUBLICATIONS
\section{PUBLICATIONS}
	\resumeSubSection{Preprints}
		\resumePubListStart
			\resumePubItem{\underline{\textbf{Zhang, R.}}, Shi, S., Jadhav, D.A., Kim, N., Brostek, A., Forester, B.R., Shukla, R., Qu, C., Kramer B., Garvin, J.L., Kleyman, T. R., Gonzalez-Vicente, A. (2024) Abnormal activation of the mineralocorticoid receptor in the aldosterone-sensitive distal nephron contributes to fructose-induced salt-sensitive hypertension. \textit{bioRxiv}}{\url{https://doi.org/10.1101/2024.08.19.608663}}
		\resumePubListEnd
	\resumeSubSection{Research Articles}
		\resumePubListStart
			\resumePubItem{Forester, B.R., \underline{\textbf{Zhang, R.}}, Schuhler, B., Brostek, A., Gonzalez-Vicente, A., Garvin, J.L. (2024) Knocking out Sodium glucose-linked transporter 5 prevents fructose-induced renal oxidative stress and salt-sensitive hypertension. \textit{Hypertension}, \textit{81}(6), 1296-1307.}{\url{https://doi.org/10.1161/HYPERTENSIONAHA.123.22535}}
			\resumePubItem{\underline{\textbf{Zhang, R.}}, Jadhav, D.A., Kim, N., Kramer, B., Gonzalez-Vicente, A., on behalf of the Kidney Precision Medicine Project. (2024) Profiling cell heterogeneity and fructose transporter expression in the rat nephron by integrating single-cell and microdissected tubule segment transcriptomes. \textit{Int. J. Mol. Sci.}, \textit{25}(5), 3071.}{\url{https://doi.org/10.3390/ijms25053071}}
			\resumePubItem{Brostek, A., Hong, N. J., \underline{\textbf{Zhang, R.}}, Forester, B. R., Barmore, L. E., Kaydo, L., Kluge, N., Smith, C., Garvin, J. L., and Gonzalez-Vicente, A. (2022) Independent Effects of Sex and Stress on Fructose-Induced Salt-Sensitive Hypertension. \textit{Physiological Reports}, \textit{10}(19), e15489.}{\url{https://doi.org/10.14814/phy2.15489}}
		\resumePubListEnd
	\resumeSubSection{Conference Abstracts}
		\resumePubListStart
			\resumePubItem{Jadhav, D. A., \underline{\textbf{Zhang, R.}}, Kramer, B. K., and Gonzalez-Vicente, A. (2024) Transcript deconvolution reveals heterogeneous cell populations in microdissected nephron segments of the rat kidney. \textit{Physiology}, \textit{39}, 831.}{\url{https://doi.org/10.1152/physiol.2024.39.S1.831}}
			\resumePubItem{\underline{\textbf{Zhang, R.}}, Shi, S., Kleyman, T. R., and Gonzalez-Vicente, A. (2023) Increased epithelial Sodium channel (ENaC) activity mediates fructose-induced salt-sensitive hypertension. \textit{Journal of the American Society of Nephrology}, \textit{34}(11S), 514.}{\url{https://doi.org/10.1681/ASN.20233411S1514c}}
			\resumePubItem{Kramer, B. K., \underline{\textbf{Zhang, R.}}, and Gonzalez-Vicente, A. (2023) Sexually dimorphic transcriptional phenotypes in tubular epithelial cells of the rat kidney. \textit{Hypertension}, \textit{80}(1S).}{\url{https://doi.org/10.1161/hyp.80.suppl_1.097}}
			\resumePubItem{\underline{\textbf{Zhang, R.}}, and Gonzalez-Vicente, A. (2023) Addition of fructose to a high-salt diet increases the expression of aldosterone-response genes. \textit{Physiology}, \textit{38}(S1).}{\url{https://doi.org/10.1152/physiol.2023.38.S1.5733301}}
			\resumePubItem{Gonzalez-Vicente, A., and \underline{\textbf{Zhang, R.}} (2023) Single-cell transcriptional phenotypes linked to anatomical localization of fructose transporters in rat proximal tubule segments. \textit{Physiology}, \textit{38}(S1).}{\url{https://doi.org/10.1152/physiol.2023.38.S1.5725750}}
			\resumePubItem{Brostek, A., Hong, N. J., \underline{\textbf{Zhang, R.}}, Forester, B. R., Barmore, L. E., Kaydo, L., Kluge, N., Smith, C., Garvin, J. L., and Gonzalez-Vicente, A. (2022) Sex and stress in fructose-induced salt-sensitive hypertension. \textit{Hypertension}, \textit{79}(1S).}{\url{https://doi.org/10.1161/hyp.79.suppl_1.076}}
		\resumePubListEnd

% Academic Service & Engagement
\section{ACADEMIC SERVICE \& ENGAGEMENT}
	\resumeSubSection{Talks}
		\resumeEngagementItemListStart
			\resumeEngagementItem{``Dissecting the Role of Dopamine in the Processing of Tactile Signals''}{2024}{Computational Neuroscience Group Meeting, Department of Biology, Emory University}
			\resumeEngagementItem{``Addition of fructose to a high-salt diet increases the expression of aldosterone-response genes''}{2023}{Renal Chalk Talks, Cleveland Kidney Center, Case Western Reserve University School of Medicine}
		\resumeEngagementItemListEnd
	\resumeSubSection{Poster Presentations}
		\resumeEngagementItemListStart
			\resumeEngagementItem{``Progression of abnormal signaling in primary somatosensory cortex of MitoPark mice''}{2025}{Larry J. Young Memorial Symposium}
			\resumeEngagementItem{``Addition of fructose to a high-salt diet increases the expression of aldosterone-response genes''}{2023}{American Physiology Summit}
			\resumeEngagementItem{``Single-cell transcriptomics linked to anatomical localization of fructose transporters in rat proximal tubule''}{2023}{American Physiology Summit}
		\resumeEngagementItemListEnd
\vspace{-8pt}

% Awards and Honors
\section{AWARDS}
	\resumeSubSection{Prizes}
		\resumeAwardItemListStart
			\resumeAwardItem{Poster Award (Zhang et al., 2025)}{Larry J. Young Memorial Symposium}{May. 2025}
			\resumeAwardItem{Abstract of Distinction (Gonzalez-Vicente \& Zhang, 2023)}{American Physiology Summit}{Apr. 2023}
			\resumeAwardItem{Outstanding Junior Award}{Case Western Reserve University}{Mar. 2022}
			\resumeAwardItem{Phi Beta Kappa Prize}{Case Western Reserve University}{Sep. 2021}
			\resumeAwardItem{Dean's High Honors}{Case Western Reserve University}{2019-2023}
		\resumeAwardItemListEnd
	\resumeSubSection{Others}
		\resumeAwardItemListStart
			\resumeAwardItem{Petit Scholar Mentor}{Petit Scholar Program, Georgia Tech/Emory CNTP}{Jan. -- Dec., 2024}
		\resumeAwardItemListEnd
\vspace{-8pt}

% Skills
\section{Skills}
	\textbf{Languages}: Chinese - Mandarin (\textit{native}), Chinese - Wu (\textit{native}), English (\textit{professional}), Spanish (\textit{Elementary})

	\textbf{Technical}: {\color{GlacierBlue}\faPython} Python, {\color{GlacierBlue}\textsc{Matlab}}, {\color{GlacierBlue}\faRProject} R, {\color{GlacierBlue}\faJava} Java, {\color{GlacierBlue}\faDatabase} MySQL, {\color{GlacierBlue}\LaTeX}, {\color{GlacierBlue} \faGitSquare} \& {\color{GlacierBlue} \faGithubSquare} Github, {\color{GlacierBlue} \faLinux} Linux \& Unix Command Line

	\textbf{Biological}: animal ethology, \textit{in vivo} electrophysiology, \textit{in vivo} multiphoton imaging, transcriptomics
\end{document}
